---
title: "DQe-c Aggregated Report"
output: 
  html_document: 
    highlight: espresso
    toc: yes
---


```{r, echo=FALSE, include=FALSE}
require(data.table);require(dplyr);require(ggplot2);require(gridExtra);require(rmarkdown);require(knitr):require(plotly);require(DT)
# detach(package:plyr) ## if plyr is installed, dplyr aggregates may not work!

path2 = "./reports" #set the path to where DQe-c report files from individual databases are saved
tables <- data.frame(tab_names=list.files(path2))
tables$type <- substr(tables$tab_names, 0,4)
```

```{r setup, include=FALSE}
opts_chunk$set(dev = 'png')
```

##The Overall Status of Missingness in Data 

### Figure 1. Overall missingness across OMOP tables and columns
The figures bolow illustrate the overall missingness ration for each column and table of latest OMOP database all together.
```{r, echo=FALSE, include=FALSE}
## DQ_M
names <- tables[(tables$type == "DQ_M"),"tab_names"]
lk1 <- list()
for (n in 1:length(names)) {
  lk1[[n]] = data.frame(read.csv(paste0(path2,"/",names[n])))
}
DQ_M <- rbindlist(lk1)
DQ_M$test_date <- as.Date(DQ_M$test_date, format = "%m/%d/%Y")

lateDQM <- aggregate(DQ_M$test_date, by = list(DQ_M$organization), max)
lateDQM$load <- paste0(lateDQM$Group.1,lateDQM$x)

DQ_M$load <- paste0(DQ_M$organization,DQ_M$test_date)

DQ_M_late <- select(subset(DQ_M,DQ_M$load %in% c(lateDQM$load)), TabNam,ColNam,test_date,FRQ,UNIQFRQ,MS1_FRQ,MS2_FRQ,MSs_PERC,organization)      

DQ_M_late_agg <- DQ_M_late %>% 
  group_by(TabNam,ColNam) %>% 
  summarise(FRQ = sum(FRQ),UNIQFRQ = sum(UNIQFRQ),MS1_FRQ = sum(MS1_FRQ),MS2_FRQ = sum(MS2_FRQ))

DQ_M_late$MSs_PERC <- (round((DQ_M_late$MS1_FRQ+DQ_M_late$MS2_FRQ)/DQ_M_late$FRQ,2))
DQ_M_late_agg$MSs_PERC <- (round((DQ_M_late_agg$MS1_FRQ+DQ_M_late_agg$MS2_FRQ)/DQ_M_late_agg$FRQ,2))
DQ_M_late_agg$test_date <- as.character(format(Sys.Date(),"%m-%d-%Y"))
DQ_M_late_agg$organization <- "agg"
```

```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 10, fig.height= 25, dpi=300}
ggplot(DQ_M_late_agg, aes(x=MSs_PERC, y=ColNam,label = MSs_PERC)) +
  geom_point(data=DQ_M_late,aes(x=MSs_PERC, y=ColNam),
             fill="gray",alpha = 0.3, shape = 15, size = 3, stroke= 0) +
  geom_point(aes(fill = MSs_PERC),alpha = 0.8, shape = 22, size = 4, stroke= 0.5) +
  # geom_text(vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  facet_wrap( ~ TabNam, scale="free_y", ncol = 1) +
  scale_fill_gradient(limits=c(0, 1),low="#FFFAF0", high="#EE2C2C", guide=F ,na.value="white")+
  theme(panel.grid.major.x = element_line(colour = "gray"),
        axis.text.x = element_text(angle = 0, hjust = 1),
        axis.text.y = element_text(angle = 0, hjust = 1)) +
  xlab("Ratio of Missing Data") + ylab("Column Name")

```


### Figure 2. Overall missingness in key indicators

```{r, echo=FALSE, include=FALSE}
###with
names <- tables[(tables$type == "with"),"tab_names"]
lk2 <- list()
for (n in 1:length(names)) {
  lk2[[n]] = data.frame(read.csv(paste0(path2,"/",names[n])))
}
with <- rbindlist(lk2)

#with$load <- paste0(with$organization,with$test_date)
with$load <- paste0(with$organization,with$test_date)

# http://genomicsclass.github.io/book/pages/dplyr_tutorial.html
late <- with %>% group_by(organization) %>% summarise(maxdate = max(as.Date(test_date, "%m-%d-%Y")))
#late <- with %>% group_by(organization) %>% summarise(maxdate = max(test_date))
#late <- with %>% group_by(organization) %>% summarise(maxdate = '10-19-2016')
late$load <- paste0(late$organization, as.character(format(late$maxdate,"%m-%d-%Y")))
#late$load <- paste0(late$organization,late$maxdate)


withlate <- select(subset(with,with$load %in% c(late$load)), group,missing,missingpop,denom,perc,organization,test_date)      

withlate_agg <- withlate %>% group_by(group) %>% summarise(missingpop = sum(missingpop),denom = sum(denom))

percent <- function(x, digits = 2, format = "f", ...) {
  paste0(formatC(x, format = format, digits = digits, ...), "%")
}

withlate_agg$missing <- round((withlate_agg$missingpop/withlate_agg$denom),4)*100
withlate_agg$perc <- percent(withlate_agg$missing)
withlate_agg$organization <- "agg"
withlate_agg$test_date <- as.character(format(Sys.Date(),"%m-%d-%Y"))
```

```{r, echo=FALSE, warning = FALSE, fig.align='center', fig.width= 10, fig.height= 10, dpi=300}
ggplot(withlate_agg, aes(x=missing,y=reorder(group,-missing),label = perc)) + 
  geom_point(aes(fill = missing),shape = 21, colour = "black",  size = 8, stroke = 3, alpha = 0.9) +
  geom_point(data=withlate, aes(x=missing,y=reorder(group,-missing)),
             shape = 21, colour = "black",  size = 4, stroke = 3, alpha = 0.3) +
  geom_text(vjust = 3, hjust = .5, nudge_y = 0, size = 4)+
  
  scale_fill_gradient(limits=c(0, 100),low="#FFFAF0", high="#EE2C2C", guide=F,na.value="white")+
  # theme_grey(base_size = base_size) + 
  labs(x = "", y = "") +
  scale_x_continuous(limits = c(0, 100)) + 
  theme_minimal() +
  theme(panel.grid.major.y = element_line(color = "gray",size = 2.5),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        axis.text.y=element_text(size=20, face="bold")) 

```


##info
This is an add-on to DQe-c report version 1.7

For questions and/or inquiries email: `hestiri@uw.edu`

#####aggregated report was generated on `r Sys.Date()` 

